Repeatability Test

### 2017-07-07 pt_characterization/rep_check/res2.tex
Draft being ready for July 10

\section{Histograms on the Second Run~\label{sec:sodb9_r2_hist}} 
This section exhibits histograms on the second run of 
INC with its task length increasing from 1 second to 4096 seconds, via SEDONA. 
The detailed description of the base data is from Table~\ref{tab:exp_notes2}.

>>>>

\section{Histograms on the Second Run~\label{sec:sodb9_r2_hist}} 
This section exhibits histograms on the second run of 
INC with its task length increasing from 1 second to 4096 seconds, via EMPv5 without Step 2. 
The detailed description of the base data is from Table~\ref{tab:exp_notes2}.

### 2017-07-07 pt_characterization/rep_check/u_s_time.tex
Draft being ready for July 10

\section{Further invstigation of the Second Run~\label{sec:u_s_time_hist}} 
This section exhibits user and system time histograms on the second run of 
INC with its task length increasing from 1 second to 4096 seconds. 
The detailed description of the base data is from Table~\ref{tab:exp_notes2}, 
and for some additional data, the corresponding description is given in Table~\ref{tab:exp_notes3}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} &  INC96$\sim$INC256 & 1000 samples, each & 2017-05-24 $\sim$ 2017-06-06 & 
Figs.~\ref{fig:ut_hist3}, \ref{fig:inc224_ut_hist}, and~\ref{fig:inc256_ut_hist}\\ \hline
					&  INC3, 6, 12, 24, 48, 72, 80, 88, 104, 112, and 120 & 1000 samples, each & 2017-06-07 $\sim$ 2017-06-16 & Figs.~\ref{fig:inc3_ut_hist}, ~\ref{fig:inc6_ut_hist}, ~\ref{fig:inc12_ut_hist}, ~\ref{fig:inc24_ut_hist},
~\ref{fig:inc48_ut_hist}, ~\ref{fig:inc72_ut_hist}, ~\ref{fig:inc80_ut_hist}, ~\ref{fig:inc88_ut_hist}, ~\ref{fig:inc104_ut_hist},~\ref{fig:inc112_ut_hist}, and~\ref{fig:inc120_ut_hist}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes4}}
\end{table}

\newpage
\subsection{User Time}

>>>>

\section{Further Investigation of the First Run and Some Additional Runs~\label{sec:u_s_time_hist}} 
This section exhibits user and system time histograms on the second run of 
INC with its task length increasing from 1 second to 4096 seconds via EMPv5 with no Step 2.
The detailed description of the base data is from Table~\ref{tab:exp_notes1}, 
and for some additional data, the corresponding description is given in Table~\ref{tab:exp_notes3}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} &  INC96$\sim$INC256 & 1000 samples, each & 2017-05-24 $\sim$ 2017-06-06 & 
Figs.~\ref{fig:ut_hist3}, \ref{fig:inc224_ut_hist}, and~\ref{fig:inc256_ut_hist}\\ \hline
					&  INC3, 6, 12, 24, 48, 72, 80, 88, 104, 112, and 120 & 1000 samples, each & 2017-06-07 $\sim$ 2017-06-16 & Figs.~\ref{fig:inc3_ut_hist}, ~\ref{fig:inc6_ut_hist}, ~\ref{fig:inc12_ut_hist}, ~\ref{fig:inc24_ut_hist},
~\ref{fig:inc48_ut_hist}, ~\ref{fig:inc72_ut_hist}, ~\ref{fig:inc80_ut_hist}, ~\ref{fig:inc88_ut_hist}, ~\ref{fig:inc104_ut_hist},~\ref{fig:inc112_ut_hist}, and~\ref{fig:inc120_ut_hist}\\ \hline
%%%%% INC2048 and INC4096 come from the second run
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes4}}
\end{table}

\subsection{Summary of Histograms}

\begin{figure}[htp!]
\vspace{-.3in}
	\centering
	\includegraphics[scale=0.5,angle=270]{u_s_time/3d_plot.eps}\label{fig:3d_plot}
	\caption{3D histograms on INC~\label{fig:hist3d}}
\end{figure}

\subsection{Absolute and Relative Variance over Increasing Task Length}

\begin{figure}[htp!]
	\centering
	\subfigure[Standard deviation (absolute)]{
		\includegraphics[scale=0.6]{u_s_time/overall_std.eps}
		\label{fig:overall_std}
	}
	\subfigure[Coefficient of variation (relative)]{
		\includegraphics[scale=0.6]{u_s_time/overall_re.eps}
		\label{fig:overall_re}
	}
	\caption{Absolute and relative variances~\label{fig:cv_inc}}
\end{figure}

\pagebreak
\newpage

\subsection{Additional Histograms}

\subsection{ET}

%\begin{figure}[hp!]
%	\centering
%	\subfigure[User time frequency on INC3]{
%		\includegraphics[scale=0.43]{u_s_time/3_sec_et_hist.eps}
%		\label{fig:inc3_ut_hist}
%	}
%	\caption{User Time Histograms of INC1 ... INC4~\label{fig:ut_hist1}}
%\end{figure}

\subsection{PT}

%\begin{figure}[hp!]
%	\centering
%	\subfigure[User time frequency on INC3]{
%		\includegraphics[scale=0.43]{u_s_time/3_sec_et_hist.eps}
%		\label{fig:inc3_ut_hist}
%	}
%	\caption{User Time Histograms of INC1 ... INC4~\label{fig:ut_hist1}}
%\end{figure}

\pagebreak
\newpage

\subsection{User Time}
